\documentclass{article}
\usepackage{fancyhdr}
\usepackage{amsmath,amssymb}
\usepackage{geometry}
\usepackage{datetime}
\usepackage{enumerate}

%Insert page formatting here
%\hoffset = -.5in
\voffset = -0.375in
%\textwidth = 6in
\textheight = 8in
\headheight = 24pt

\pagestyle{fancy}

\rhead{Peter Olson\\Student ID: $441666$}
\lhead{Math 3200\\Homework 1}
\chead{\today}
\cfoot{}

%\addtolength{\headwidth}{\marginparsep}
%\addtolength{\headwidth}{\marginparwidth}

%\renewcommand{\labelitemi}{$\diamond$}

\renewcommand{\labelitemi}{$\diamond$}
\renewcommand{\implies}{\rightarrow}
\newcommand{\widespace}{\qquad \qquad \;}
\newcommand{\tret}{\\ \hline}
\newcommand{\fh}{\tfrac{1}{2}}
\newcommand{\deriv}[2]{\frac{d #1}{d #2}}
\newcommand{\pderiv}[2]{\frac{\delta #1}{\delta #2}}
\newcommand{\vr}{\vec{r}}
\newcommand{\at}{\text{ at }}

\begin{document}
\section*{Exercise 2.6}
In a state lottery game, you must match all 6 numbers drawn at random from 1 to 54 without replacement to win the grand prize, 5 out of 6 numbers to win the second prize, and 3 out of 6 numbers to win the third prize. The order of the numbers is irrelevant. Find the probability of winning each prize.

\subsection*{Answer}
Let the probability of some event occurring be fundamentally be described as $P(A) = \frac{M}{N}$, that is, the probability of some outcome $A$ be $M$ number of outcomes that affirm $A$ out of all the totally possible outcomes $N$. To win a grand prize (let this be $A_1$), $N$ is the combination of all possible winning sets for some ticket of six numbers. Only one outcome, that is, $M$, achieves $A$, so that the player wins a grand prize. Therefore, the probability that a player wins a grand prize is:
\begin{align*}
	P(A_1) &= \frac{1}{\binom{54}{6}} = \frac{1}{25827165} \\
	P(A_1) &= 3.87\times 10^{-8}
\end{align*}
In layman's terms, next to no chance. For the second place prize (let this be $A_2$), there are six different combinations of the numbers on the card (i.e. $\binom{6}{5}$ ) that might win, again out of $\binom{54}{6}$ possible numbers.
\[ P(A_2) = \frac{\binom{6}{5}}{\binom{54}{6}} = 2.32 \times 10^{-7} \]
Marginally better, but still not great. For the third place prize (let this be $A_3$), there are $\binom{6}{4}$ numbers on the card that might win, again out of $\binom{54}{6}$ possible numbers.
\[ P(A_3) = \frac{\binom{6}{4}}{\binom{54}{6}} = 5.81 \times 10^{-7} \]
Great news for the state! Having to pay out an of the first, second, and third highest prizes is an extremely unlikely occurrence.
\end{document}